\documentclass{resume} % Use the custom resume.cls style
\usepackage{soul}
\usepackage{textcomp}
\usepackage[left=0.30in,top=0.27in,right=0.30in,bottom=0.27in]{geometry} %Document margins
\usepackage[T1]{fontenc}
\usepackage{comment}
\usepackage[utf8]{inputenc}
\usepackage{tgpagella}
\usepackage{hyperref}
\usepackage[dvipsnames]{xcolor}
\definecolor{darkcerulean}{rgb}{0.03, 0.27, 0.49}
\definecolor{dark-blue}{rgb}{0.15,0.15,0.4}
\definecolor{carmine}{rgb}{0.59, 0.0, 0.09}
\definecolor{ceruleanblue}{rgb}{0.16, 0.32, 0.75}
\definecolor{medium-blue}{rgb}{0,0,0.5}
\definecolor{harvard-red}{rgb}{0.79, 0.0, 0.09}

\usepackage{enumitem}
\hypersetup{
	colorlinks, %Colours links instead of ugly boxes
	urlcolor     = medium-blue, %Colour for external hyperlinks
	linkcolor    = medium-blue, %Colour of internal links
	citecolor   = medium-blue %Colour of citations
}

\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\hypersetup{
    colorlinks=true,           % Use colors for links instead of borders
    linkcolor=harvard-red,     % Color of internal links
    citecolor=harvard-red,     % Color of citations
    urlcolor=harvard-red,      % Color of URLs
    pdfborder={0 0 0},         % No border around links
    pdfborderstyle={}          % Ensure no underline or special border style
}



\vspace{-0.2cm}\name{Alfonso Merendino \vspace{-0.15cm}} % Your name

\address{Hardenbergstrasse 23, Frankfurt am Main, Germany 60327} % Address
\address{(+39) 338 288 4553 ~~~ \href{mailto:alfonso.merendino@yale.edu}{alfonso.merendino@yale.edu}} % Contact details

\begin{document}

	%----------------------------------------------------------------------------------------
	%\ EDUCATION SECTION
	%----------------------------------------------------------------------------------------
	\vspace{-0.2cm}
	\begin{rSection}{EDUCATION}
		{\large \textsc{\textbf{Yale University}}} \hfill {New Haven, CT(US)}
		\\
\textit{Ph.D. in Economics} \hfill \textit{2026 - 2031}

		\vspace{0.1cm}
		{\large \textsc{\textbf{Bocconi University}}} \hfill {Milan (Italy)}
		\\
\href{https://www.unibocconi.it/en/programs/master-science/economic-and-social-sciences}{\textit{M.Sc. in Economic and Social Sciences (ESS)}} \hfill\textit{2022 - 2025}
		\vspace{-0.15cm}
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Final Grade: 110/110 \textit{cum laude}. \ul{GPA: 29.5/30.0}.}
%			\item \small {Selected among top-ranked students for taking the Ph.D. course in Probability Theory (Grade: 29/30).}
			\item \small {Ph.D. courses: "Probability Theory I" from the program in Statistics and Computer Science (Grade: 29/30), and \\ Prof. T. Monacelli's second-year Ph.D. course "Advanced Macroeconomics IV" (audited).}
			\item \small {Thesis: \textit{Supply Chain Uncertainty, Energy Prices and Inflation}. Advisor: Prof. T. Monacelli.}
		\end{itemize}
\href{https://www.unibocconi.it/en/programs/bachelor-science/economic-and-social-sciences}{\textit{B.Sc. in Economic and Social Sciences (BESS)}} \hfill \textit{2019 - 2022}
		\vspace{-0.15cm}
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Final Grade: 110/110 \textit{cum laude}. \ul{GPA: 29.6/30.0}.}
			\item \small {Thesis: \textit{Coexistence of Temporary and Permanent Contracts: An Empirical Approach using Survival Analysis}. \\
Advisor: Prof. T. M. Boeri.} 
		\end{itemize}
		\vspace{0.2cm}
		{\large \textsc{\textbf{New York University}}} \hfill {New York, NY (US)}
		\\
		\textit{Visiting Student, Department of Economics} \hfill \textit{Spring 2022}
		\vspace{-0.15cm}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Selected for Exchange Program with a single slot available among 100+ applicants. GPA: 3.96/4.0.}
			\item \small {Ph.D. courses: "Stochastic Calculus" at the Courant Mathematics Department (Grade: A-).}
		\end{itemize}
		\vspace{0.2cm}
		{\large \textsc{\textbf{Liceo Classico G. Garibaldi}}} \hfill {Palermo (Italy)}
		\\
		\textit{5-year Italian high school diploma in Classical Studies} \hfill \textit{2014 - 2019}
		\vspace{-0.15cm}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Final Grade: 100/100 \textit{cum laude}. Graduated in top 1.6\% nationwide.}
		\end{itemize}
	\end{rSection}

\vspace{0.2cm}
	%----------------------------------------------------------------------------------------
	%\ WORK EXPERIENCE
	%----------------------------------------------------------------------------------------
	\begin{rSection}{WORK EXPERIENCE}
		{\large \textsc{\textbf{European Central Bank}}} \hfill {Frankfurt am Main (Germany)}
		\\
		\textit{Trainee in Macroeconomic Modeling in the Euro Area External Sector and Euro Adoption Division} \hfill \textit{Sep 2025 - Present}
		\vspace{-0.15cm}
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Co-authoring with Carlos Montes-Galdón and Nicolò Gnocato a research project on tariffs, supply chain uncertainty, and inflation.}
			\item \small {Country expert for the quarterly macroeconomic projections for Latvia.}
		\end{itemize}

		\vspace{0.1cm}
		{\large \textsc{\textbf{Harvard University}}} \hfill {Milan (Italy)}
		\\
		\textit{Research Assistant to Prof. S. Stantcheva} \hfill \textit{Aug 2023 - May 2025}
		\vspace{-0.15cm}
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Contributed to research using large-scale household surveys to understand people’s preferences about inflation, trade, and other economic policies. Tasks included writing survey questions, collecting responses (Qualtrics), and data analysis (Python, RStudio, Stata).}
			\item \small {Conducted extensive literature reviews, analyzing both theoretical and empirical articles.}
		\end{itemize}

		\vspace{0.1cm}
		\textit{Social Economics Lab, \href{https://socialeconomicslab.org/social-economics-lab-about/}{Research Fellow}} \hfill \textit{Aug 2023 - Present} \\
	
	\vspace{-0.15cm}
		{\large \textsc{\textbf{Bocconi University}}} \hfill {Milan (Italy)}
		\\
		\textit{Research Assistant to Prof. T. Monacelli} \hfill \textit{Febr 2025 - Jul 2025}
		\vspace{-0.15cm}
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Assisted research on tariffs and monetary policy, and on flight from dollar. Drafted model extensions and calibrated the model using Dynare.}
		\end{itemize}
		\vspace{0.2cm}
		\textit{Academic Fellow: Teaching Assistant to Prof. T. Monacelli and Prof. L. Iovino} \hfill \textit{Aug 2024 - Feb 2025}
		\vspace{-0.15cm}
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Prepared lecture slides for Prof. Tommaso Monacelli’s second-year Ph.D. course "Advanced Macroeconomics IV."}
			\item \small {Wrote lecture notes, exams, and graded assignments for the intermediate-level undergraduate course "Macroeconomics and Economic Policy" taught by Prof. L. Iovino within the B.Sc. in Economic and Social Sciences.}
		\end{itemize}
		\vspace{0.2cm}
		\textit{Research Assistant to Prof. M. P. Squicciarini} \hfill \textit{Jun - Oct 2021}
		\vspace{-0.15cm}
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Contributed to a research project in Economic History. Analyzed data with Stata and proposed changes to the model. Prepared monthly presentations on LaTeX and discussed the findings.}
		\end{itemize}
		\vspace{0.2cm}
		{\large \textsc{\textbf{IGIER (Innocenzo Gasparini Institute for Economic Research)}}} \hfill {Milan (Italy)}
		\\
		\textit{IGIER Researcher and Visiting Student (Mentor: Prof. T. Monacelli)} \hfill \textit{Feb 2023 - Apr 2025}
		\vspace{-0.15cm}
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Worked on several independent research projects, with a focus on models, mathematical derivations, and calibrations using Dynare. Extensively reviewed the literature on the effects of nominal and real rigidities in New Keynesian models.} 
		\end{itemize}


		\vspace{0.2cm}
		{\large \textsc{\textbf{Northwestern Kellogg University}}} \hfill {Milan (Italy)}
		\\
		\textit{Research Assistant to Prof. N. Persico} \hfill \textit{Jul 2024 - Dec 2025}
		\vspace{-0.15cm}
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Contributed to several research projects using large-scale surveys. Wrote survey questions, collected responses (Qualtrics), and analyzed data (Stata) using Principal Component Analysis and Structural Equation Modeling. Collaborated on drafting a theoretical model of people’s tastes for freedom.}

		\end{itemize}
	\end{rSection}

\vspace{0.2cm}
	%----------------------------------------------------------------------------------------
	%\ WORKING PAPERS
	%----------------------------------------------------------------------------------------
	\begin{rSection}{WORKING PAPERS}
Supply Chain Uncertainty, Energy Prices, and Inflation. with T. Monacelli
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
%			\item \small {This paper seeks to rationalize the exceptional pass-through of energy price shocks to inflation and the extreme supply chain volatility observed during 2021–2023. It develops a New Keynesian model with supply chain uncertainty, where heightened supply chain volatility causes energy prices to act as signals of costly supply chain disruptions for firms. These estimated supply chain shocks further drive firms to increase their optimal output prices, amplifying inflation.}
			\item \small {Between 2021 and 2023, inflation showed an exceptionally strong and persistent response to energy price shocks, amid unprecedented volatility in transportation disruptions along global supply chains. We propose a theory of supply shocks in which supply chain \textit{uncertainty} amplifies the transmission of energy price shocks to inflation. We provide empirical evidence in support of the theory and outline a New Keynesian model with supply chain uncertainty to formalize the core mechanism.}
			\item \small { Presented at the \textit{Money, Macro and Finance Society Annual Conference 2025} (Reading University), and at the Macroeconomic seminar on October 9th (Paris School of Economics). }
		\end{itemize}

\href{https://www.brunoleoni.it/wp-content/uploads/2023/12/IBL-SR-Gare_Gas.pdf}{How the gas market changes. The economic effects of liberalization of the gas distribution market in Italy}, with C. Amenta and C. Stagnaro (policy writing).
		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
		\begin{itemize}\itemsep=-0.2cm
			\item \small {Policy brief of the Italian Think Tank Istituto Bruno Leoni assessing the economic benefits from the liberalization of the gas distribution market in Italy, underlining the current obstacles to further liberalization of the market. }
\item \small {Presented the policy brief to a large panel of MPs, CEOs of leading gas distribution firms, and experts.}
		\end{itemize}
	\end{rSection}

\vspace{0.2cm}
	%----------------------------------------------------------------------------------------
	%\ CERTIFICATIONS, LANGUAGE & IT SKILLS
	%----------------------------------------------------------------------------------------
	\begin{rSection}{CERTIFICATIONS, LANGUAGE \& IT SKILLS}
		\textbf{GRE General Test}. Q165 (70\textsuperscript{th} percentile), V161 (86\textsuperscript{th} percentile), AWA 4.5 (83\textsuperscript{rd} percentile) - \textit{Oct 2024}.
		
		\textbf{Languages}: Italian (native), English (excellent, TOEFL: 106/120, Oct 2024), Spanish (fair).
		
		\textbf{Computer Skills}: Stata, \LaTeX, Qualtrics, Microsoft Office (excellent command). Python, MATLAB, Dynare (very good command). R, EViews (good command).
	\end{rSection}

\vspace{0.2cm}
	%----------------------------------------------------------------------------------------
	%\ AWARDS AND SCHOLARSHIPS
	%----------------------------------------------------------------------------------------
	\begin{rSection}{AWARDS AND SCHOLARSHIPS}
		\textbf{Zegna Founder’s Scholarship} \hfill \textit{2026}
		\\ Scholarship to fund travel, research, and living expenses (\texteuro 10,000).

		\textbf{Bocconi Graduate Merit Award} \hfill \textit{2022 - 2025}
		\\ Merit-based full tuition waiver for Bocconi M.Sc. programs (\texteuro 28,000).
		
		\textbf{Registered into Albo Nazionale delle Eccellenze} \hfill \textit{2019}
		\\ List of Italian high school students graduating cum laude drafted by the Italian Ministry of Education.
	\end{rSection}

\vspace{0.2cm}
%----------------------------------------------------------------------------------------
% EXTRA-CURRICULAR ACTIVITIES SECTION
%----------------------------------------------------------------------------------------
\begin{rSection}{EXTRA-CURRICULAR ACTIVITIES}

\textbf{Harvard Business School Online.} Course in Alternative Investments (\textit{Jun-Jul 2021})

\textbf{Cuora Concept.} Volunteering student association to publish a briefs on \href{https://www.cuoraconsulting.org/cuora-concept-blog/inflation-benefits-of-no-involvement-of-the-government-in-monetary-policy}{Central Bank Credibility and Inflation} (\textit{2020-2021}). Managed the transition of the organization from a student association to a volunteer non-profit company.
\end{itemize}

\textbf{Fellow at Economic Society for Bocconi Students (\textit{2022-present})}
%		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
%\begin{itemize}
%    \item \small Fellow (\textit{2022 -present}). Participated to seminars and discussions with leading scholars in different fields of economics.
%\end{itemize}

\textbf{Corporate Hangar (Prysmian).} Rotational program across the business advisory teams and development of a startup idea in energy distribution (\textit{Jun-Jul 2022}). 


%		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
%\begin{itemize}
 %   \item \small Successfully participated to a course on principles of finance and .
%\end{itemize}



\textbf{Mediterranea Junior Golf Academy  (\textit{2012 - 2019}). HCP: 2 (54 is beginner; 0 is professional)}

%		\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
%\begin{itemize}
  %  \item \small Won several events of the Italian Junior Golf Season and participated in international events (\textit{2012 - 2019}). HCP: 2 (54 is beginner; 0 is professional).
 %   \item \small Professional Caddie for Mr. Chris Doak at the 2017 Rocco Forte Open Verdura (European Tour).
%\end{itemize}

\end{rSection}

\end{document}

